Unit tests

### 2018-03-08 Tests.Rmd
minor changes to Tests.Rmd

#***basic tests of the function using kendall-preserving surrogates
datcop<-claytonCopula(5,2)
numpts<-1000
m<-rCopula(numpts,datcop)
plot(m[,1],m[,2],type='p')
rect(0,0,1,1)

@@

plot(res[,1,1],res[,2,1],type='p') #should look like a Gumbel
rect(0,0,1,1)
BiCopGofTest(res[,1,1],res[,2,1],family=4) #should indicate an acceptable fit
BiCopGofTest(res[,1,2],res[,2,2],family=4) #should indicate an acceptable fit
BiCopGofTest(res[,1,3],res[,2,3],family=4) #should indicate an acceptable fit

@@

#basic tests using spearman preserving surrogates
res<-copsurrog2d(m,tarcop,'spearman',3)
dim(res)
if (sum(dim(res)[1:2]==dim(m))==2)
{
  print("passed")
} else
{
  print("dim of output is wrong")
}

@@

#see how the skewness of the spatial average
#is affected
source("SkewnessAnd3CentMom.R")
skdat<-myskns(apply(FUN=mean,X=d,MARGIN=1)) #skewness of spatial mean of data
mnres<-apply(FUN=mean,X=sur,MARGIN=c(1,3)) 
sksur<-apply(FUN=myskns,X=mnres,MARGIN=2) #skewnesses of spatial means of surrogate datasets
sum(sksur<skdat)/length(sksur) #skewnesses of surrogs should be less than that of data
range(sksur) #these should mostly be negative
skdat #this should be positive

>>>>

#***basic tests of the function using kendall-preserving surrogates
datcop<-claytonCopula(5,2)
numpts<-1000
m<-rCopula(numpts,datcop)
plot(m[,1],m[,2],type='p',asp=1)
rect(0,0,1,1)

@@

plot(res[,1,1],res[,2,1],type='p',asp=1) #should look like a Gumbel
rect(0,0,1,1)
BiCopGofTest(res[,1,1],res[,2,1],family=4) #should indicate an acceptable fit
BiCopGofTest(res[,1,2],res[,2,2],family=4) #should indicate an acceptable fit
BiCopGofTest(res[,1,3],res[,2,3],family=4) #should indicate an acceptable fit

@@

#***basic tests using spearman preserving surrogates
res<-copsurrog2d(m,tarcop,'spearman',3)
dim(res)
if (sum(dim(res)[1:2]==dim(m))==2)
{
  print("passed")
} else
{
  print("dim of output is wrong")
}

@@

#see how the skewness of the spatial average
#is affected
source("SkewnessAnd3CentMom.R")
skdat<-myskns(apply(FUN=mean,X=d,MARGIN=1)) #skewness of spatial mean of data
mnres<-apply(FUN=mean,X=sur,MARGIN=c(1,3)) 
sksur<-apply(FUN=myskns,X=mnres,MARGIN=2) #skewnesses of spatial means of surrogate 
                                          #datasets
sum(sksur<skdat)/length(sksur) #skewnesses of surrogs should be less than that of data
range(sksur) #these should mostly be negative
skdat #this should be positive
